Tabular Constraint Learning

### 2016-04-04 Paper/ECAI/tabular.tex
ADDED THE FIGURE

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage[numbers]{natbib}
\usepackage{notoccite}

@@

\sergey{to himself we need structure here}

>>>>

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}

@@

\sergey{to himself we need structure here} 
\begin{figure}[thpb]
  \begin{center}
    \includegraphics[width=0.55\textwidth]{figures/Demo.png}
  \end{center}
  \vspace{-10pt}
  \caption{An example of constraint reconstruction (in blue) with indicated groups (in green)}
  \label{fig:main_example}
\end{figure}

\section{Formalization}

\newcommand{\constraints}{\ensuremath{\mathcal{C}}\xspace}
\newcommand{\generategroups}{\textit{generateGroups}\xspace}
\newcommand{\extractgroups}{\textit{extractGroups}\xspace}
\newcommand{\findassignment}{\textit{findAssignment}\xspace}

\begin{algorithm}[thb]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $D$ -- dataset, (optional groups $G$)
    \State \textbf{Output:} $S$ -- learned constraints with their satisfaction assignment
    \If{$G$ is not defined}
       \State $G \gets \extractgroups(D)$
    \EndIf
  \For{$c \in \constraints$} \Comment{\constraints -- the set of predefined Excel constraints}
    \For{$G_1, \dots, G_n \in \generategroups(c,G)$}
      \State $S \gets S \cup \findassignment(c, G1, \dots, G_n)$
    \EndFor
  \EndFor\\
\Return $S$
\end{algorithmic}
\caption{First Order Model: Iterative Query Enumeration}
\label{algo:top_cycle}
\end{algorithm}

\section{Case Study aka Experiments}
